### 2016-06-29 GPCE2016/sections/Implementation.tex

Disciplined use of Classless Java (avoiding class
declarations as done in Section~\ref{sec:ep}) illustrates what \emph{pure} IB is like.
However, using \mixin, CB and IB programming can be mixed together,
harvesting the practical convenience of using existing Java libraries, the full
Java language, and IDE support.
The key to our implementation is compilation agents, which
 allows us to rewrite the Java AST just
before compilation. We discuss advantages and limitations of our approach.

>>>>

Disciplined use of Classless Java (avoiding class
declarations as done in Section~\ref{sec:ep}) illustrates what \emph{pure} IB is like.
However, using \mixin, CB and IB programming can be mixed together,
harvesting the practical convenience of using existing Java libraries, the full
Java language and IDE support.
The key to our implementation is compilation agents, which
 allows us to rewrite the Java AST just
before compilation. We discuss advantages and limitations of our approach.

### 2016-06-29 GPCE2016/sections/Overview.tex

\begin{lstlisting}
interface Point2D { int x(); int y();
    static Point2D of(int _x, int _y){ return new Point2D(){
        int x=_x; int y=_y;
        public int x(){return x;}   public int y(){ return y; }
        Point2D withX(int val){ return Point2D.of(val,this.y()); }
        Point2D withY(int val){ return Point2D.of(this.x(),val); }
    }; }
  Point2D withX(int val);    Point2D withY(int val); }
\end{lstlisting}
\end{comment}
Moreover, if the programmer wants a different implementation, they may
provide an alternative implementation using \Q@default@ methods. For example:
\begin{lstlisting}
@Obj interface Point2D {
    int x(); int y();
    default Point2D withX(int val){ /*myCode*/ }
    Point2D withY(int val); }
\end{lstlisting}

@@

\paragraph{Property updater as Injections}

By declaring fields in Newspeak and other languages,
the programmers specifies field signatures and (critically) the intention of storing such information. Then the language generate getter and setter.
Once state is abstracted away,
it is well known that is possible to replace state
access with computation, but the type of the field stays the same.

Our fluid approach to state is specular:
the intention of storing the information is not expressed by the programmer and set in stone, 
but can vary by inheritance:
We generate the idea of the field
just starting from getters and setters signatures.

In this case, we leverage on our fluid state to changing the underling type of the field,
 and our \Q@with@ is providing
the right injection from the old type to the new one.

>>>>

\begin{lstlisting}
interface Point2D { int x(); int y();
    static Point2D of(int _x, int _y){ return new Point2D(){
        int x=_x; int y=_y;
        public int x(){return x;}   public int y(){ return y; }
        Point2D withX(int val){ return Point2D.of(val,this.y()); }
        Point2D withY(int val){ return Point2D.of(this.x(),val); }
    }; }
  Point2D withX(int val);    Point2D withY(int val); }
\end{lstlisting}
\end{comment}
Moreover, if the programmer wants a different implementation, he may
provide an alternative implementation using \Q@default@ methods. For example:
\begin{lstlisting}
@Obj interface Point2D {
    int x(); int y();
    default Point2D withX(int val){ /*myCode*/ }
    Point2D withY(int val); }
\end{lstlisting}

@@

% \paragraph{Property updater as Injections}

% By declaring fields in Newspeak and other languages,
% the programmers specifies field signatures and (critically) the intention of storing such information. Then the language generate getter and setter.
% Once state is abstracted away,
% it is well known that is possible to replace state
% access with computation, but the type of the field stays the same.

% Our fluid approach to state is specular:
% the intention of storing the information is not expressed by the programmer and set in stone, 
% but can vary by inheritance:
% We generate the idea of the field
% just starting from getters and setters signatures.

% In this case, we leverage on our fluid state to changing the underling type of the field,
%  and our \Q@with@ is providing
% the right injection from the old type to the new one.
